The pollination trade-off

### 2018-11-10 paper/manuscript.Rmd
Updated change summary and to-do list

* Use AICc instead of AIC (no change in results)
* To keep signature of phenology, absolute flower counts (log-transformed) are used instead of relative abundances
* Columns in the trait matrix for phenology are scaled so that it doesn't count 5 times as much as other traits
* Only modeling open and bagged pollen counts, using the bagged as a control. So not showing the results of the relative pollen count (open vs bagged flowers) anymore
* Introduced visit efficiency instead of share in the pollen pool as it is a better predictor. 
* Use a PCA of the explanatory variables to understand different plant strategies

@@

* References to the introduction
* Discussion from bullet-points to actual paragraphs. I will do that once we all agree with the quantitative methodology and getting some contributions for the interpretation of the results
* Spell-check everything
* Write the abstract

@@

* __Originality__: Currently the plants phenology are included in the traits. The relative abundance of the plant in each of the five a survey months is included as a trait. This allows to maintain the model simple and it could be easily argued that phenological strategy can be considered as another trait. However I'm not convinced that it is a good idea to keep them together, especially because differences in phenology is a rather intuitive factor/strategy to overcome competition for pollination. Do you think I should separate traits from phenology? If yes, should I use the same "originality" approach to determine how different each species is? 
* __Traits__: Currently I don't mention much traits in the discussion. I think the trait component is valuable and interesting but sadly at the moment the data quality is poor. Only 4 traits have been compiled: growth form, longevity, flower colour, and whether the plant is native to the region. It won't be possible to gather all of the traits used by @coux_linking_2016-1 from the literature but hopefully it is for a good proportion of them. Daniel and Jason, could we discuss options here? 
* __Conspecific pollen__: Previously I used, as Hugo did in his papers, the gain in conspecific pollen in open flowers relative to the amount of in bagged flowers as the indication of the "quantity" of the pollination service. After thinking more about the limitations of this metric (pollinators also take pollen from stigmas, some plants are not self-fertile, different maturation times for male/female organs, etc.) I decided it would be best to include both the total and the relative pollen amounts in the manuscript. This add more nuance to the story and interpretation which is not cool, but I think together they overcome each other's problems. What do you think about it?
* __Naming__: I currently use absolute and relative pollen gain as names for the two previous metrics. I think it's OK but I feel there might be better options. Any ideas?
* __Quantity & quality__: This version of the paper uses quantity/quality to frame the results. I think that's pretty neat. However, different studies define quantity and quality in different ways. Hugo for example used the relative amount of conspecific pollen as an indication of quantity and the amount of heterospecific pollen for quality. We discussed earlier that a good indication could be the _proportion_ of heterospecific pollen instead. What do you think? Should I ditch quantity/quality and stick to conspecific/heterospecific pollen instead? Should I stay with the current definitions of quantity and quality of pollination? This probably needs meeting/Skype, but it would be good to think about it.
* __Pollen transfer__: Currently all I'm using from the pollen transfer networks is the share of a plant in the pollen pool. That fits nice with the density hypothesis but its rather simplistic. Any ideas? 
* __Pollen in bagged flowers__: Jason, you mentioned that pollen in bagged flowers can be due to selfing or wind. You meant wind moving flowers and that causing pollen to be deposited on stigmas? Wouldn't that count as selfing too?

>>>>

* Now using AICc instead of AIC to evaluate models (no change in results)
* Changes to traits: (*a*) to keep signature of phenology, absolute flower counts (log-transformed) are used instead of relative abundances. Also, now (*b*) columns in the trait matrix for phenology are scaled so that it doesn't count 5 times as much as other traits.
* The absolute/relative/gain terminology was confusing. Now  I'm modeling open and bagged pollen counts directly, using the bagged as a sort of control.
* Introduced visit efficacy instead of share in the pollen pool as a predictor in the model. Turns out to be a better predictor and also incorporates quantitative visitation data which was missing from the previous models. 
* Now I use a PCA of the explanatory variables to understand different plant strategies. 
* Introduction has been rewritten to be more *hypothesis* oriented. The manuscript also includes references thorughout.
* Added abstract

@@

* Spell-check everything
* Decide on a journal. Manuscript is currently written for an interdisciplinary one.

@@

* __Traits__: Currently I don't mention much traits in the discussion. I think the trait component is valuable and interesting but sadly at the moment the data quality is poor. Only 4 traits have been compiled: growth form, longevity, flower colour, and whether the plant is native to the region. It won't be possible to gather all of the traits used by @coux_linking_2016 from the literature but hopefully it is for a good proportion of them. Daniel and Jason, could we discuss options here?
